Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-11-16 index.qmd
adding fundings and code availability

The authors would like to thank the extensive revisions and comments made by anonymous reviewers to improve the work. This work was supported through the BiCOME (Biodiversity of the Coastal Ocean: Monitoring with Earth Observation) project funded by the European Space Agency under the ‘Earth Observation Science for Society’ element of FutureEO-1 BIODIVERSITY+PRECURSORS call, contract No. 4000135756/21/I-EF. This work was also supported by French Ministry of Research & Higher Education for funding first authors PhD. Further, this work was partially funded by Portuguese national funds through the FCT—Foundation for Science and Technology, I.P., under the individual project/contract CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM (UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).

>>>>

The authors would like to thank the extensive revisions and comments made by anonymous reviewers to improve the work. This work was supported through the BiCOME (Biodiversity of the Coastal Ocean: Monitoring with Earth Observation) project funded by the European Space Agency under the ‘Earth Observation Science for Society’ element of FutureEO-1 BIODIVERSITY+PRECURSORS call, contract No. 4000135756/21/I-EF. This work was also supported by French Ministry of Research & Higher Education for funding first authors PhD. Ana I. Sousa funded by Portuguese national funds through the FCT—Foundation for Science and Technology, I.P., under the individual project/contract CEECIND/00962/2017 and by FCT/MCTES through the support to CESAM (UIDB/50017/2020+UIDP/50017/2020+LA/P/0094/2020).
